Liptschiz

### 2024-02-20 lipschitz/valabstraction.tex
update plots

\begin{tikzpicture}[
	declare function={
		f(\x,\y)=max((\x+\y),0)-max(\x,0);
	}]
	\begin{axis}[axis lines=center,
		axis on top,
		set layers=default,
		xrange=-3:3,
		yrange=-2:2,
		unit vector ratio=1 1 1,% <- HERE (taken from Phelype Oleinik's deleted answer)
		scale=3 %<- added to compensate for the downscaling
		% resulting from unit vector ratio=1 1 1
		]
		\addplot3[
		domain=-3:3,
		domain y=-1:1,
		samples=40,
		samples y=40,
		surf,
		] {f(\x,\y)};
	\end{axis}
\end{tikzpicture}

>>>>

\hspace*{-20ex}

\begin{tikzpicture}
	\begin{axis}[axis lines=center,
				axis on top,
				set layers=default,
				xrange=-5:5,
				yrange=-2:2,
				unit vector ratio=1 1 1, scale=1.5,
				view={45}{40},
				]
		\addplot3[	surf,] 
		coordinates {
	 (0,0,0) (-1,1,0) (-4,1,0) (-4,-1,0) (0,-1,0) (0,0,0)
		};

		\addplot3[	surf,	] 
		coordinates { (0,0,0) (0,1,1) (4, 1, 1) (4, -1, -1) (1,-1,-1) (0,0,0)
		};

		\addplot3[	surf,	] 
		coordinates { (0,0,0)  (-1,1,0) (0,1,1) (0,0,0)
		};

			\addplot3[	surf,	] 
		coordinates { (0,0,0)  (0,-1,0) (1,-1,-1) (0,0,0)
		};

	\end{axis}
\end{tikzpicture}

%\begin{tikzpicture}[
%	declare function={
%		f(\x,\y)=max((\x+\y),0)-max(\x,0);
%	}]
%	\begin{axis}[axis lines=center,
%		axis on top,
%		set layers=default,
%		xrange=-3:3,
%		yrange=-2:2,
%		unit vector ratio=1 1 1,% <- HERE (taken from Phelype Oleinik's deleted answer)
%		scale=3 %<- added to compensate for the downscaling
%		% resulting from unit vector ratio=1 1 1
%		]
%		\addplot3[
%		domain=-3:3,
%		domain y=-1:1, surf,
%		samples=40,
%		samples y=40,
%		] {f(\x,\y)};
%	\end{axis}
%\end{tikzpicture}
